---
title: "Lecture 3 - 9-11"
output: html_document
---

# Notes about formatting Markdown files 

There are three major components to this file:
*1) YAML header: The segment at the beginning of the document bracketed by ---s.
*2) Text + inline R: Written text with simple formatting like # heading,  **bold**, and _italic_ (enter inline code by typing '`r`' + 'format()' )
*3) Code chunks: Blocks of code surrounded by ``` (enter by pressing option+command+I) and name the code chunks {r chunk_name}. 
*4) 'knitr' = knitting, which combines text, formatting, and code 


# create a dataframe containing a sample of size 500 from a random normal variable and the absolute value of each element of the sample

```{r}
library(tidyverse)

ls_df = tibble(
  norm_samp = rnorm(500), 
  abs_norm_samp = abs(norm_samp)
)

ggplot(ls_df, aes(x = abs_norm_samp)) + geom_histogram () # make a histogram of the absolute value of each element in the sample

round(median(ls_df$abs_norm_samp), digits=2) #median of the variable containing absolute values rounded to 2 decimal places is 
```

# to customize code chunk formatting
*eval = FALSE: code will be displayed but not executed; results are not included.
*echo = FALSE: code will be executed but not displayed; results are included.
*include = FALSE: code will be executed but not displayed; results are not included.
*message = FALSE and warning = FALSE: prevents messages and warnings from being displayed.
*results = hide and fig.show = hide: prevents results and figures from being shown, respectively.
*collapse = TRUE: output will be collapsed into a single block at shown at the end of the chunk.

*error: errors in code will stop rendering when FALSE; errors in code will be printed in the doc when TRUE. The default is FALSE and you should almost never change it.

# Find mean and median
```{r}
mean(ls_df$norm_samp)
median(ls_df$norm_samp)

```

# to create diff types of document 
html_document:           
    toc: true
    toc_float: true
    
output:                   
  word_document: default

output:                   
  pdf_document: default


